Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-13 paper/main.tex
minor changes until statistical analysis

% intro
Lastly, we algorithmically annotated the temporal
structure of low-level perceptual features to create nuisance regressors.
% visual shit
For the AV stimulus, we computed the mean luminance of a movie frame
(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
half, the difference in mean luminance of the lower and upper half, and finally
the perceptual differene of consecutive frames.
% auditory shit
Finally, we computed the left-right difference in volume and root mean
square energy averaged across the length of every movie frame (\unit[40]{ms}) of
both audio-tracks.

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events [lenght = 20 ms?].\todo{actually, that might not be
true}

AV:
% convolving

AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.

% AD: null regressors
If a stimulus segment did not contain an event of a category, a null regressor
was chosen for that category in that segment.
% AV: null regressor
As for the regressors for AD stimulus, a null regressor was chosen for a
regressor in a segment if that segment did not contain an event of the
corresponding category.

% convolving
Events for all regressors of the AV and AO timulus were convolved with a
double gamma hemodynamic response function (HRF).
% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

\paragraph{regressor correlations}

% stimuli not designed for research purposes
The audio-description and the movie were not designed to be used in a BOLD fMRI
experiment but to entertain their audiences.
% fixed time course; detection power
Since we annotated events in fixed time courses that could not experimentally
manipulated, regressors that are based on these events could be correlated
leading to shared variance and thus low detection power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we first tested for correlation of regressors across the eight segments
of each stimulus and correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of regressors of the same stimulus [which suggest the models should
not suffer from low detection power due to shared variance among regressors].
% correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli. This was expected and served as ``sanity check'' since the
audio-track of the audio-description is the audio-track of the movie but
featuring the additional narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

\paragraph{included regressors}

% AO events in AV

% AV events in AO

>>>>

% intro
Lastly, we algorithmically annotated the temporal structure of low-level
perceptual features to create nuisance regressors.
% visual shit
For the AV stimulus, we computed the mean luminance of a movie frame
(\unit[40]{ms}), the difference in mean luminance of each frame's left and right
half, the difference in mean luminance of the lower and upper half, and finally
the perceptual difference of consecutive frames.
% auditory shit
Finally, we computed the left-right difference in volume and root mean square
energy averaged across the length of every movie frame (\unit[40]{ms}) of both
audio-tracks.

@@

% movie events
The events of the movie cut related categories and \texttt{no\_cut} events were
modeled as impulse events [lenght = 20 ms?].\todo{actually, that might not be
true}.
%
Nouns were modeled from onset to offset of each word, low-level confounds from
onset to offset of the corresponding movie frame AO:
% modeling as boxcar function
Events were were modeled as boxcar function from onset to offset of each word.
% convolving
Events for all regressors of the AV and AO stimulus were convolved with a double
gamma hemodynamic response function (HRF).
% we checked correlations
Since the time-series of modeled hemodynamic activity were based on events in
stimuli that were not designed for research, we then tested if time-series were
correlated (i.e. share variance) leading to low detection power in subsequent
analyses\todo{pick your favorite}.
% fixed time course; detection power
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Since we annotated events in fixed time courses that could not experimentally
manipulated, the modeled time-series [of hemodynamic activity] based on these
events could be correlated leading to shared variance and thus low detection
power of subsequent analyses.
% correlations within stimuli and across stimuli
Hence, we tested for correlation of regressors across the eight segments of each
stimulus and also for correlations of regressors across both stimuli (s. Figure
\ref{fig:reg-corr})
% correlations within each stimulus
The computed Pearson correlation coefficients demonstrate no to minor
correlations of modeled hemodynamic time-series belonging to the same stimulus.
% correlations across stimuli
The highest correlations are apparent between auditory low-level confounds
across stimuli (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
\texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749). This was
expected and served as ``sanity check'' since the audio-track of the
audio-description is the audio-track of the movie but featuring the additional
narrator (s. Figure \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
As a result, we felt encouraged to create voxel-wise GLM $t$-contrasts similarly
to previous studies that used controlled stimuli.

@@

\paragraph{Design Matrix}

\todo[inline]{I created the part "design matrix" cause following parts are
usually written in the "regressor paragraph" in publications but do not really
fit in the subsection above}

% null regressors
If a stimulus segment did not contain an event of a category (e.g. no event of
\texttt{vpe\_old} in segment 3 of the movie; cf. Table \ref{tab:ao-events}), a
null regressor was chosen for that category in that segment.

% temporal derivatives
Temporal derivatives were included in the design matrix to compensate for
regional differences between modeled and actual HRF \citep{friston1998event}.
% motion parameters
Six motion parameters were also used as additional nuisance regressors.
% high-pass filtering
Finally, designs were filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.
